Uncovering Distributed System Bugs\\ during Testing (not Production!)

### 2015-08-18 overview.tex
updates in overview

\subsection{Finding bugs in distributed systems}
\label{sec:overview:bugs}

Due to the asynchronous nature of message passing, message handlers can potentially interleave in arbitrary order. To complicate matters further, random failures are the norm in distributed systems that operate in production: nodes might fail at any moment in a cluster, and thus programmers have to implement sophisticated mechanisms that can deal with these failures and appropriately recover the state of the system. Also, with multicore machines becoming a commodity nowadays, individual components of a distributed system are commonly implemented using multithreaded code, which adds another source of nondeterminism.

To be able to efficiently find bugs in a distributed system and deterministically reproduce them, a testing tool must provide three key capabilities: capturing all sources of nondeterminism; injecting faults in arbitrary interleavings; and exploring all possible interleavings in a systematic fashion. Traditional testing techniques used by product groups, although focus on stressing the system and randomly injecting faults, they are typically unable to capture and control all sources of nondeterminism, which makes them ineffective in finding the most tricky of bugs.

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{img/azurestore}
\caption{High-level architecture of a distributed extent management system for Windows Azure.}
\label{fig:azurestore}
\end{figure}

>>>>

\subsection{Testing distributed systems}
\label{sec:overview:bugs}

In a distributed system, message handlers can interleave in arbitrary order, because of the asynchronous nature of message-based communication. To complicate matters further, unexpected failures are the norm in production: nodes in a cluster might fail at any moment, and thus programmers have to implement sophisticated mechanisms that can deal with these failures and recover the state of the system. Moreover, with multicore machines having become a commodity, individual components of a distributed system are commonly implemented using multithreaded code, which adds another source of nondeterminism.

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{img/azurestore}
\caption{Top-level components of a distributed extent management system for Windows Azure.}
\label{fig:azurestore}
\end{figure}

All these sources of nondeterminism (as well as nondeterminism due to timeouts, message losses and client requests) can easily create \emph{heisenbugs}~\cite{musuvathi2008finding}, which are corner-case bugs that are difficult to detect, diagnose and fix, without using advanced \emph{asynchrony-aware} testing techniques.
%
The ideal testing tool should be able to work on unmodified systems, capture and control all possible sources of nondeterminism, systematically inject faults in the right places, and explore all feasible execution paths. However, this is easier said than done when testing production systems.

\subsection{Bugs in distributed systems}
\label{sec:overview:bugs}

There are two types of properties that developers of distributed systems are mostly interested in testing: \emph{safety} and \emph{liveness} properties. A safety property holds if it is \emph{always} satisfied, i.e. holds invariantly in every program state during execution. Likewise, a liveness property holds if it becomes \emph{eventually} satisfied, i.e. it will hold at some program state during execution. A safety or liveness property violation means that there is a bug that should be fixed.

Examples ...
